Qeury-Driven Central Slot-Values Extraction for Wikipedia Entities at Web Scale

### 2013-11-04 paper/flairs27/content/introduction.tex
first half milenko's comments

In this paper we develop an efficient query-driven slot value extraction for certain wikipedia entities from a timely stream of documents on internet. Entities from three categories of \textit{person}, \textit{organization} and \textit{facility} are considered. This can be regarded as an automatic way to expand and automate Wikipedia citation system and a way to automatically populate knowledge bases such as freebase. The challenges that we address are the scale, precision and recall of the extent we can extract slot values from internet for entities of interest. Examples of these facts are 'Who a person has met during a certain period of time?', 'Who are the employees of this organization?', 'Who has met who in this facility at a certain time?'

 An important challenge in maintaining Wikipedia.org (WP), the most popular web-based, collaborative, multilingual knowledge base on the internet, is making sure its contents are up-to-date. Presently, there is considerable time lag between the publication date of cited news and the date of an edit to WP creating the citation. The median time lag for a sample of about 60K web pages cited by WP articles in the \textit{living\_people} category is over a year and the distribution has a long and heavy tail \cite{JFrank12}. Also, the majority of WP entities have updates on their associated article much less frequently than their mention frequency. Such stale entries are the norm in any large knowledge base (KB) because the number of humans maintaining the KB is far fewer than the number of entities. %Further, the number of mentions is much larger than the number of entities~\cite{JFrank12}. 
Reducing latency keeps KBs such as WP relevant and helpful to it users.

Given an entity page, possible citations may come from a variety of sources. The actual citable information is a small percentage of the total documents that appear on the web. We develop a system to read streaming data and filter out articles that are candidates for citations. Given these documents, we extract the pairs of information in the article that is recommended for citations for each entity page in  WP. Some of the challenges that we face in this regard includes: having to balance between infamous and obscure enitities, ambiguous entities (entities of exact same name that are differnet in real life), facts that can very broad (e.g. things that an entity is affiliated with) or very specific (such as cause of death of a \textit{person} entity).

Our system contains three main components. First, we pre-process the data and build models representing the knowledge base entries. Next, we use the models to filter a stream of documents so they only contain 
candidate recommendations. Lastly, we processes sentences from candidate extractions and return specific information to be cited. The system can handle infrequent entities, but adding of new entities requries going thorugh full dataset.

In this paper, we describe the system we built to process the data. We built this system as part of a formal task described in Section~\ref{sec:kbatask}. Our approach to this task is to build a modular system
that allows us to explore the nuances of the training data and queries. Overall, we contribute the following:
\begin{itemize}[noitemsep,nolistsep]
\item Introduce a method to build models of name variations (Section \ref{section:aliasgeneration});
\item Built a system to filter a large amount of diverse documents (Section~\ref{sec:ccrimpl});
\item Extract entity-slot-value triples of information to be added to KB (Section~\ref{sec:ssve});
\item Filter the final results using deduplication and inference (Section~\ref{section:highAccuracyFilter});
\item Self-evaluate our results over a 4.5 TB data set (Section\ref{sec:results}).
\end{itemize}

% Evaluation Criteria

>>>>

In this paper we develop an efficient query-driven slot value extraction for given Wikipedia.org (WP) entities from a timely stream of documents on internet as they are being created. Slot value extraction is formally defined as follows: match each sentence to the generic sentence structure of [\textit{Subject} - \textit{Verb} - \textit{Adverbial/Complement}]\cite{sentencePatterns08}, where  \textit{Subject} represents the entity and \textit{Verb} is the relation type we are interested in (e.g. Table~\ref{table:slotNameOntology}). If a sentence matches these two components of the sentence pattern, \textit{Adverbial/Complement} would be returned as the other side of the relation (which we refer to as slot value). Slot value extraction is a challenging task in current state of the art Knowldge Bases (KB). Popular graphical KB such as Freebase or DBPedia keep data in structured format where entities are connected via relationships (\textit{Verb}) and the associated attributes (\textit{Adverbial/Compelement}). Our system can be used to automatically populate such KBs or even fill-in the information boxes at entity WP page itself.

Entities from three categories of \textit{person}, \textit{organization} and \textit{facility} are considered. The challenges that we address are: first finding documents that contain useful information about the entity (avoid spams, documents that do not have direct information about the entity even though they mention them, etc), the scale where \textit{stream processing} nature of the system makes it suitable to avoid batch processing natures of Hadoop and operate in the realm of streams such as twitter storm\footnote{http://storm-project.net/} which similarly processes unblounded streams of twitter data or Spark Streaming \footnote{http://spark.incubator.apache.org/}. As other Natural Language Processing tasks, precision and recall of the extent we can extract slot values are very important metrics that we will discuss later on. Having to balance between infamous and obscure enitities, dealing with slots that can be very broad (e.g. things that an entity is affiliated with) or very specific (such as cause of death of a \textit{person} entity).

To take on an example assume we are analyzing a sentence from the internet such as "\underline{Boris Berezovsky} made his fortune in Russia in the 1990s when the country went through privatisation of state property and 'robber capitalism', and passed away March 2013.". First we have to pay attemtion that there are two \textit{Boris Berezovsky} entities in WP, one a businessman and the other a pianist. Any slot value extraction shall take this into account and try to come up with a viable distinguishing policy (Entity Resolution). Then, we match the sentence to find a slot value such as \textit{DateOfDeath} valued at March 2013. Other examples that this system can answer could be 'Who a person has met during a certain period of time?', 'Who are the employees of this organization?', 'Who has met who in this facility at a certain time?'.

 An important challenge in maintaining WP, the most popular web-based, collaborative, multilingual KB on the internet, is making sure its contents are up-to-date. Presently, there is considerable time lag between the publication date of cited news and the date of an edit to WP creating the citation. The median time lag for a sample of about 60K web pages cited by WP articles in the \textit{living\_people} category is over a year and the distribution has a long and heavy tail \cite{JFrank12}. Also, the majority of WP entities have updates on their associated article much less frequently than their mention frequency. Such stale entries are the norm in any large KB because the number of humans maintaining the KB is far fewer than the number of entities. %Further, the number of mentions is much larger than the number of entities~\cite{JFrank12}. 
Reducing latency keeps KBs and WP relevant and helpful to its users. Given an entity page, possible citations may come from a variety of sources. The actual citable information is a small percentage of the total documents that appear on the web. We develop a system to read streaming data and filter out articles that are candidates for citations.

Our system contains three main components. First, we pre-process the data and build models representing the KB entries. Next, we use the models to filter a stream of documents so they only contain candidate citations. Lastly, we processes sentences from candidate extractions and return slot values. 
% EITHER SAY WHAT IT MEANS OR GIVE EXAMPLES OR COMMENT IT
%We build a modular system that allows us to explore the nuances of the training data and queries. 
Overall, we contribute the following:
\begin{itemize}[noitemsep,nolistsep]
\item Introduce a method to build models of name variations
\item Built a system to filter a large amount of diverse documents
\item Extract, infer and filter entity-slot-value triples of information to be added to KB 
\end{itemize}

\begin{table}
\caption{Ontology of Slots }
\centering
\label{table:slotNameOntology}

\begin{tabular}{|c|c|c|}
\hline 
\textbf{PER} & \textbf{FAC} & \textbf{ORG} \\ 
\hline 
\begin{tabular}{@{}l@{}}Affiliate \\ AssociateOf \\ Contact\_Meet\_PlaceTime \\ AwardsWon \\ 
DateOfDeath \\ 
CauseOfDeath\\
Titles\\
FounderOf\\
EmployeeOf\end{tabular}
  &
   \begin{tabular}[b]{l}Affiliate \\ Contact\_Meet\_Entity \end{tabular} 
   & 
   \begin{tabular}{@{}l@{}}Affiliate \\ TopMembers \\ FoundedBy\end{tabular} \\ 
\hline 
\end{tabular} 
\end{table}
% Evaluation Criteria

### 2013-11-04 paper/flairs27/content/system.tex
first half milenko's comments

\section{System Overview}

In this section, we introduce the main components of the system. Our system is built with a pipeline architecture in mind giving it the advantage to run each section separately to allow stream processing without blocking the data flow of components (Figure~\ref{fig:system}). The three logical components include sections for performing preprocessing to prepare the required data, Cumulative Citation Recommendation to annotate cite-worthy documents, Streaming Slot Filling to generate the actual slot values and PostProcessing to increase precision/recall. We work on a streaming data set and entities are from Twitter or WP to query.

@@

As mentioned before the time lag from an event occurance until it is cited in WP is in average over a year due to the fact that human maintainers are much less than the number of entities in WP and that the frequency of news update on entities escalates this difference. Hence having an automatic way to extract this knowldge for entities can be a very valuable asset.

@@

\begin{figure*}
  \centering
%  \includegraphics[width=6in]{./images/sdl-eps-converted-to.pdf}
  \includegraphics[width=6in]{./images/System_Diagram_with_model_Vertical.pdf}
% http://convert.neevia.com/pdfconvert/
  \vspace*{-.1in} 
  \caption{The GatorDSR team System Architecture.
  Components are logically groups with dotted boxes.
  Color details the programing language implementation of components.}
  \label{fig:system}
  \vspace*{-.2in}
\end{figure*}

\textit{Preprocessing.}
The contest prohibits Wikipedia entities to have any manual aliases being added and only allows automatic ways. We use Wikipedia API backlink references (redirects to a wiki entity) as aliases of the entity. We also extract aliases from within the text of a wiki entity, which will be described in Section~\ref{section:aliasgeneration}. This whole process is referred to as \textit{Alias Extraction}. The manual extraction rule is lifted and participants are allowed to manually add aliases for Twitter entities. This is allowed because the Twitter website does not provide an example page from the beginning of the document stream. This process of extracting aliases for Twitter entities is referred to as \textit{Manual Alias Extraction}.

Once aliases are available we pass them through rules of generating proper name orders which will produce various forms of writing a name. As a basic example Bill Gates can be written as Gates, Bill. This will allow the system to capture various notation forms of aliases. We refer to this part as \textit{Name Order Generator}.

>>>>

\section{System}

In this section, we introduce the main components of the system. Our system is built with a pipeline architecture in mind giving it the advantage to run each section separately to allow stream processing without blocking the data flow of components (Figure~\ref{fig:system}). The three logical components include sections on \textit{Model} for entity resolution purposes, \textit{Wiki Citation} to annotate cite-worthy documents, \textit{Slot Filling} to generate the actual slot values.

@@

@@

\begin{figure}
  \centering
%  \includegraphics[width=6in]{./images/sdl-eps-converted-to.pdf}
  \includegraphics[width=3in]{./images/System_Diagram_with_model_Vertical-crop.pdf}
% http://convert.neevia.com/pdfconvert/
  \vspace*{-.1in} 
  \caption{System Architecture.
  Components are logical groups noted with dotted boxes.}
  \label{fig:system}
  \vspace*{-.2in}
\end{figure}

\subsection{Model}

We use Wikipedia API to get these aliases automatically. This is done by retrieving backlink references (redirects of a wiki entity), e.g. William Henry Gates is an alias for Bill Gates in WP as a backlink reference. Unfortunately this is not good enough and to enhance recall we need more aliases. To have better use of a wiki page we parse HTML DOM of the page, then use regular expressions to extract the bold phrases of the first paragraph as alias of the actual entity. Based on our observation this is a very accurate heuristic and provides us with lots of famous aliases of the entities. As an example of when this might not wirk, is that there might be occasions that some other topic is written in bold typesetting in the first paraph apart from the entity aliases itself but these are very rare.

Once aliases are available we pass them through rules of generating proper name orders which will produce various forms of writing a name. As a basic example Bill Gates can be written as Gates, Bill also. This will allow the system to capture various notation forms of aliases. We refer to this part as \textit{Alias Order Generator}.
